---
title: "GHSI Score Converter"
description: "Convert GHSI, GHSI-AO, and PGSI scores to harm categories, ICECAP-A and
  SF-6D tariffs.\n"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(jsonlite)
library(tidyverse)

# Read lookup table -- update this CSV to change the conversion data
lookup <- read_csv("data/GHSI_Rasch_Lookup_2026-02-10.csv", show_col_types = FALSE)

# De-duplicate for the GHSI lookup (indexed by GHSI10_estimate 0-30)
# Some rows are duplicated when PGSI scores share a GHSI10 estimate
lookup_ghsi <- lookup %>%
  distinct(GHSI10_estimate, .keep_all = TRUE) %>%
  arrange(GHSI10_estimate)

# Build JSON array for GHSI conversions, indexed by GHSI10_estimate (0-30)
js_rows <- lookup_ghsi %>%
  rowwise() %>%
  mutate(
    js = paste0(
      '{ ghsi7: ', ifelse(is.na(GHSI7_score), 'null', GHSI7_score),
      ', ghsi7_10_precise: ', ifelse(is.na(GHSI7_10_precise), 'null', sprintf("%.2f", GHSI7_10_precise)),
      ', ghsi7_10_lower: ', ifelse(is.na(GHSI7_10_lower), 'null', sprintf("%.2f", GHSI7_10_lower)),
      ', ghsi7_10_upper: ', ifelse(is.na(GHSI7_10_upper), 'null', sprintf("%.2f", GHSI7_10_upper)),
      ', ghsi3: ', ifelse(is.na(GHSI3_score), 'null', GHSI3_score),
      ', ghsi3_10_precise: ', ifelse(is.na(GHSI3_10_precise), 'null', sprintf("%.2f", GHSI3_10_precise)),
      ', ghsi3_10_lower: ', ifelse(is.na(GHSI3_10_lower), 'null', sprintf("%.2f", GHSI3_10_lower)),
      ', ghsi3_10_upper: ', ifelse(is.na(GHSI3_10_upper), 'null', sprintf("%.2f", GHSI3_10_upper)),
      ', category: "', GHSI_Category, '"',
      ', icecap: ', sprintf("%.2f", ICECAP),
      ', icecap_dis: ', sprintf("%.2f", ICECAP_disutility),
      ', sf6d: ', sprintf("%.2f", SF6D),
      ', sf6d_dis: ', sprintf("%.2f", SF6D_disutility),
      ' }'
    )
  ) %>%
  pull(js)

lookup_json <- paste0("[\n    ", paste(js_rows, collapse = ",\n    "), "\n  ]")

# Build separate PGSI lookup array, indexed by PGSI score (0-27)
pgsi_rows <- lookup %>%
  filter(!is.na(PGSI_score)) %>%
  arrange(PGSI_score) %>%
  rowwise() %>%
  mutate(
    js = paste0(
      '{ pgsi: ', PGSI_score,
      ', ghsi10: ', GHSI10_estimate,
      ', pgsi_10_precise: ', sprintf("%.2f", PGSI_10_precise),
      ', pgsi_10_lower: ', sprintf("%.2f", PGSI_10_lower),
      ', pgsi_10_upper: ', sprintf("%.2f", PGSI_10_upper),
      ', category: "', GHSI_Category, '"',
      ', icecap: ', sprintf("%.2f", ICECAP),
      ', icecap_dis: ', sprintf("%.2f", ICECAP_disutility),
      ', sf6d: ', sprintf("%.2f", SF6D),
      ', sf6d_dis: ', sprintf("%.2f", SF6D_disutility),
      ' }'
    )
  ) %>%
  pull(js)

pgsi_json <- paste0("[\n    ", paste(pgsi_rows, collapse = ",\n    "), "\n  ]")

# Read GHSI-AO lookup table for Affected Others
lookup_ao <- read_csv("data/GHSI-AO_Lookup_2026-02-11.csv", show_col_types = FALSE)

# Build JSON array for GHSI-AO conversions, indexed by GHSIAO10_estimate (0-30)
ao_rows <- lookup_ao %>%
  arrange(GHSIAO10_estimate) %>%
  rowwise() %>%
  mutate(
    js = paste0(
      '{ ao7: ', ifelse(is.na(GHSIAO7_score), 'null', GHSIAO7_score),
      ', ao7_10_precise: ', ifelse(is.na(GHSIAO7_10_precise), 'null', sprintf("%.2f", GHSIAO7_10_precise)),
      ', ao7_10_lower: ', ifelse(is.na(GHSIAO7_10_lower), 'null', sprintf("%.2f", GHSIAO7_10_lower)),
      ', ao7_10_upper: ', ifelse(is.na(GHSIAO7_10_upper), 'null', sprintf("%.2f", GHSIAO7_10_upper)),
      ', ao3: ', ifelse(is.na(GHSIAO3_score), 'null', GHSIAO3_score),
      ', ao3_10_precise: ', ifelse(is.na(GHSIAO3_10_precise), 'null', sprintf("%.2f", GHSIAO3_10_precise)),
      ', ao3_10_lower: ', ifelse(is.na(GHSIAO3_10_lower), 'null', sprintf("%.2f", GHSIAO3_10_lower)),
      ', ao3_10_upper: ', ifelse(is.na(GHSIAO3_10_upper), 'null', sprintf("%.2f", GHSIAO3_10_upper)),
      ', category: "', GHSIAO_Category, '"',
      ', icecap: ', sprintf("%.2f", ICECAP),
      ', icecap_dis: ', sprintf("%.2f", ICECAP_disutility),
      ', sf6d: ', sprintf("%.2f", SF6D),
      ', sf6d_dis: ', sprintf("%.2f", SF6D_disutility),
      ' }'
    )
  ) %>%
  pull(js)

ao_json <- paste0("[\n    ", paste(ao_rows, collapse = ",\n    "), "\n  ]")
```

This tool converts scores from different versions of the Gambling Harms Severity Index ([**GHSI-3**](items.html#ghsi), [**GHSI-7**](docs/items.html#ghsi), or [**GHSI-10**](items.html#ghsi)) into a GHSI harm category and estimated health utility tariffs on the [ICECAP-A](https://www.bristol.ac.uk/population-health-sciences/projects/icecap/icecap-a/) and SF-6D scales. The Affected Others tab provides the same conversions for the Affected Others ([**GHSI-AO-3**](items.html#ghsi-ao), [**GHSI-AO-7**](items.html#ghsi-ao), or [**GHSI-AO-10**](items.html#ghsi-ao)) versions. You can also convert **PGSI** (Problem Gambling Severity Index) scores to GHSI-10 equivalents using the Alternative Measures tab. If you enter a shorter-form or alternative measure score, it will first be converted to a GHSI-10 (or GHSI-AO-10) equivalent.

<style type="text/css">
.converter-container {
  max-width: 680px;
  margin: 0 auto;
  padding: 0 1rem;
}
.converter-form {
  background: #fff9ef;
  border: 1px solid rgba(0, 0, 0, 0.1);
  border-radius: 8px;
  padding: 2rem;
  margin-bottom: 2rem;
}
.form-group {
  margin-bottom: 1.5rem;
}
.form-group label {
  display: block;
  font-family: "Hanken Grotesk", sans-serif;
  font-weight: 600;
  font-size: 0.95rem;
  margin-bottom: 0.5rem;
  color: #252323;
}
.radio-group {
  display: flex;
  gap: 1.5rem;
  margin-top: 0.25rem;
}
.radio-group label {
  display: flex;
  align-items: center;
  gap: 0.4rem;
  font-weight: 400;
  cursor: pointer;
  font-size: 1rem;
}
.radio-group input[type="radio"] {
  accent-color: #EB6534;
  width: 16px;
  height: 16px;
  cursor: pointer;
}
.score-input-row {
  display: flex;
  align-items: center;
  gap: 1rem;
}
.score-input-row input[type="number"] {
  width: 100px;
  padding: 0.6rem 0.8rem;
  font-family: "Bitter", serif;
  font-size: 1.1rem;
  border: 2px solid rgba(0, 0, 0, 0.15);
  border-radius: 6px;
  background: white;
  color: #252323;
  transition: border-color 0.2s;
}
.score-input-row input[type="number"]:focus {
  outline: none;
  border-color: #EB6534;
}
.score-range-hint {
  font-size: 0.85rem;
  color: rgba(37, 35, 35, 0.6);
}
.convert-btn {
  font-family: "Hanken Grotesk", sans-serif;
  padding: 0.75rem 2rem;
  background-color: #698F3F;
  color: #E6EFE9;
  border: none;
  border-radius: 6px;
  font-size: 1rem;
  font-weight: 600;
  cursor: pointer;
  transition: all 0.2s ease;
  display: block;
  width: 100%;
}
.convert-btn:hover {
  background-color: #5a7835;
  transform: translateY(-1px);
  box-shadow: 0 4px 8px rgba(105, 143, 63, 0.3);
}
.convert-btn:active {
  transform: translateY(0);
}
.results-panel {
  display: none;
  margin-top: 2rem;
}
.results-panel.visible {
  display: block;
}
.result-card {
  background: white;
  border: 1px solid rgba(0, 0, 0, 0.1);
  border-radius: 8px;
  padding: 1.5rem 2rem;
  margin-bottom: 1rem;
  border-left: 4px solid #698F3F;
}
.result-card h3 {
  font-family: "Hanken Grotesk", sans-serif;
  font-size: 0.85rem;
  text-transform: uppercase;
  letter-spacing: 0.05em;
  color: rgba(37, 35, 35, 0.5);
  margin: 0 0 0.25rem 0;
  font-weight: 600;
}
.result-card .result-value {
  font-family: "Bitter", serif;
  font-size: 1.4rem;
  font-weight: 600;
  color: #252323;
  margin: 0;
}
.result-card .result-detail {
  font-size: 0.9rem;
  color: rgba(37, 35, 35, 0.65);
  margin: 0.25rem 0 0 0;
}
.result-card.category-card {
  border-left-color: #EB6534;
}
.category-no-harm { border-left-color: #698F3F; }
.category-low-harm { border-left-color: #E8B931; }
.category-moderate-harm { border-left-color: #EB6534; }
.category-high-harm { border-left-color: #C1292E; }
.category-severe-harm { border-left-color: #6B1D24; }
.category-badge {
  display: inline-block;
  padding: 0.25rem 0.75rem;
  border-radius: 4px;
  font-family: "Hanken Grotesk", sans-serif;
  font-weight: 600;
  font-size: 1rem;
  color: white;
}
.badge-no-harm { background-color: #698F3F; }
.badge-low-harm { background-color: #E8B931; color: #252323; }
.badge-moderate-harm { background-color: #EB6534; }
.badge-high-harm { background-color: #C1292E; }
.badge-severe-harm { background-color: #6B1D24; }
.results-grid {
  display: grid;
  grid-template-columns: 1fr 1fr;
  gap: 1rem;
}
@media (max-width: 600px) {
  .results-grid {
    grid-template-columns: 1fr;
  }
  .score-input-row {
    flex-direction: column;
    align-items: flex-start;
  }
}
.ghsi10-conversion-note {
  font-size: 0.9rem;
  color: rgba(37, 35, 35, 0.65);
  margin-top: 0.15rem;
}
.error-message {
  color: #C1292E;
  font-size: 0.9rem;
  margin-top: 0.5rem;
  display: none;
}
.error-message.visible {
  display: block;
}
d-article .converter-container a,
d-article .converter-form a {
  border-bottom: none;
}
d-article .converter-container input,
d-article .converter-container button,
d-article .converter-container label {
  border-bottom: none;
}
.converter-tabs {
  display: flex;
  flex-wrap: wrap;
  gap: 0;
  margin-bottom: 0;
}
.converter-tab {
  font-family: "Hanken Grotesk", sans-serif;
  font-weight: 600;
  font-size: 0.95rem;
  padding: 0.75rem 1.25rem;
  border: 1px solid rgba(0, 0, 0, 0.1);
  border-bottom: none;
  border-radius: 8px 8px 0 0;
  background: #f0ece4;
  color: rgba(37, 35, 35, 0.5);
  cursor: pointer;
  transition: all 0.2s ease;
}
.converter-tab:hover {
  background: #f5f0e8;
}
.converter-tab.active {
  background: #fff9ef;
  color: #252323;
  border-bottom: 1px solid #fff9ef;
  margin-bottom: -1px;
  position: relative;
  z-index: 1;
}
d-article .converter-tab {
  border-bottom: none;
}
.converter-form.tabbed {
  border-radius: 0 8px 8px 8px;
}
.tab-panel {
  display: none;
}
.tab-panel.active {
  display: block;
}
</style>

<div class="converter-container">
<div class="converter-tabs">
<button class="converter-tab active" id="tab-ghsi" type="button">GHSI Versions</button>
<button class="converter-tab" id="tab-ao" type="button">Affected Others</button>
<button class="converter-tab" id="tab-alt" type="button">Alternative Measures</button>
</div>
<div class="converter-form tabbed">
<div class="tab-panel active" id="panel-ghsi">
<div class="form-group">
<label>Which GHSI version are you converting from?</label>
<div class="radio-group">
<label><input type="radio" name="ghsi-version" value="ghsi3" /> GHSI-3</label>
<label><input type="radio" name="ghsi-version" value="ghsi7" checked /> GHSI-7</label>
<label><input type="radio" name="ghsi-version" value="ghsi10" /> GHSI-10</label>
</div>
</div>
<div class="form-group">
<label for="score-input" id="score-label">Enter your GHSI-7 score</label>
<div class="score-input-row">
<input type="number" id="score-input" min="0" max="21" step="1" placeholder="0" />
<span class="score-range-hint" id="range-hint">Valid range: 0 &ndash; 21</span>
</div>
<p class="error-message" id="error-msg"></p>
</div>
<button class="convert-btn" id="convert-btn" type="button">Convert Score</button>
</div>
<div class="tab-panel" id="panel-ao">
<div class="form-group">
<label>Which GHSI-AO version are you converting from?</label>
<div class="radio-group">
<label><input type="radio" name="ao-version" value="ao3" /> GHSI-AO-3</label>
<label><input type="radio" name="ao-version" value="ao7" checked /> GHSI-AO-7</label>
<label><input type="radio" name="ao-version" value="ao10" /> GHSI-AO-10</label>
</div>
</div>
<div class="form-group">
<label for="ao-score-input" id="ao-score-label">Enter your GHSI-AO-7 score</label>
<div class="score-input-row">
<input type="number" id="ao-score-input" min="0" max="21" step="1" placeholder="0" />
<span class="score-range-hint" id="ao-range-hint">Valid range: 0 &ndash; 21</span>
</div>
<p class="error-message" id="ao-error-msg"></p>
</div>
<button class="convert-btn" id="ao-convert-btn" type="button">Convert Score</button>
</div>
<div class="tab-panel" id="panel-alt">
<div class="form-group">
<label for="pgsi-score-input">Enter your PGSI score</label>
<div class="score-input-row">
<input type="number" id="pgsi-score-input" min="0" max="27" step="1" placeholder="0" />
<span class="score-range-hint">Valid range: 0 &ndash; 27</span>
</div>
<p class="error-message" id="pgsi-error-msg"></p>
</div>
<button class="convert-btn" id="pgsi-convert-btn" type="button">Convert Score</button>
</div>
</div>
<div class="results-panel" id="results-panel">
<div class="result-card category-card" id="category-card">
<h3 id="category-heading">GHSI Harm Category</h3>
<p class="result-value"><span class="category-badge" id="category-badge"></span></p>
</div>
<div class="result-card" id="ghsi10-card" style="display: none;">
<h3 id="ghsi10-heading">GHSI-10 Equivalent Score</h3>
<p class="result-value" id="ghsi10-value"></p>
<p class="result-detail ghsi10-conversion-note" id="ghsi10-detail"></p>
</div>
<div class="results-grid">
<div class="result-card">
<h3>ICECAP-A Tariff</h3>
<p class="result-value" id="icecap-value"></p>
<p class="result-detail">Disutility: <span id="icecap-disutility"></span></p>
</div>
<div class="result-card">
<h3>SF-6D Tariff</h3>
<p class="result-value" id="sf6d-value"></p>
<p class="result-detail">Disutility: <span id="sf6d-disutility"></span></p>
</div>
</div>
</div>
</div>

## Understanding Health Utility and Disutility

The ICECAP-A and SF-6D scores shown above are measures of *health utility*. Health utility is a standard approach in health economics and is routinely used by NICE and the NHS to assess whether interventions are clinically meaningful and represent good value for money.

Health utility is a way of measuring quality of life on a scale from 0 to 1. A score of 1 represents full health and wellbeing, while 0 represents a state considered equivalent to death. In UK population studies, average scores are typically around 0.86 on the ICECAP-A and 0.90 on the SF6D ([see research publications](papers.html#reports)).

These measures allow gambling harms to be understood in the same way as other long-term conditions, enabling direct comparison with mental health disorders, addictions, and chronic illness.

We use two complementary measures because gambling harms affect people in different ways:

- **ICECAP-A** captures broader capability and life functioning, including stability, relationships, achievement, enjoyment and independence.

- **SF-6D** focuses more specifically on health-related quality of life, including physical functioning, pain, mental health and energy.

**Disutility** refers to the reduction in wellbeing compared to a healthy population. As GHSI (or GHSI-AO) scores increase (indicating greater harm), health utility scores decrease.


In practical terms, a 2–3 point change on the GHSI corresponds to changes in quality of life that meet accepted thresholds for clinical meaningfulness in NICE-aligned health-economic evaluation."



```{r converter-js, results='asis'}
cat(paste0('
<script type="application/javascript">
(function() {

  // --- Data lookups ---
  var LOOKUP = ', lookup_json, ';
  var PGSI_LOOKUP = ', pgsi_json, ';
  var AO_LOOKUP = ', ao_json, ';

  var GHSI7_TO_GHSI10 = {};
  var GHSI3_TO_GHSI10 = {};
  for (var i = 0; i < LOOKUP.length; i++) {
    if (LOOKUP[i].ghsi7 !== null) {
      GHSI7_TO_GHSI10[LOOKUP[i].ghsi7] = i;
    }
    if (LOOKUP[i].ghsi3 !== null) {
      GHSI3_TO_GHSI10[LOOKUP[i].ghsi3] = i;
    }
  }

  var AO7_TO_AO10 = {};
  var AO3_TO_AO10 = {};
  for (var i = 0; i < AO_LOOKUP.length; i++) {
    if (AO_LOOKUP[i].ao7 !== null) {
      AO7_TO_AO10[AO_LOOKUP[i].ao7] = i;
    }
    if (AO_LOOKUP[i].ao3 !== null) {
      AO3_TO_AO10[AO_LOOKUP[i].ao3] = i;
    }
  }

  var PGSI_BY_SCORE = {};
  for (var i = 0; i < PGSI_LOOKUP.length; i++) {
    PGSI_BY_SCORE[PGSI_LOOKUP[i].pgsi] = PGSI_LOOKUP[i];
  }

  // --- Tab elements ---
  var tabs = [
    { tab: document.getElementById("tab-ghsi"), panel: document.getElementById("panel-ghsi") },
    { tab: document.getElementById("tab-ao"),   panel: document.getElementById("panel-ao") },
    { tab: document.getElementById("tab-alt"),  panel: document.getElementById("panel-alt") }
  ];

  // --- GHSI form elements ---
  var versionRadios = document.querySelectorAll(\'input[name="ghsi-version"]\');
  var scoreInput = document.getElementById("score-input");
  var scoreLabel = document.getElementById("score-label");
  var rangeHint = document.getElementById("range-hint");
  var convertBtn = document.getElementById("convert-btn");
  var errorMsg = document.getElementById("error-msg");

  // --- AO form elements ---
  var aoVersionRadios = document.querySelectorAll(\'input[name="ao-version"]\');
  var aoScoreInput = document.getElementById("ao-score-input");
  var aoScoreLabel = document.getElementById("ao-score-label");
  var aoRangeHint = document.getElementById("ao-range-hint");
  var aoConvertBtn = document.getElementById("ao-convert-btn");
  var aoErrorMsg = document.getElementById("ao-error-msg");

  // --- PGSI form elements ---
  var pgsiScoreInput = document.getElementById("pgsi-score-input");
  var pgsiConvertBtn = document.getElementById("pgsi-convert-btn");
  var pgsiErrorMsg = document.getElementById("pgsi-error-msg");

  // --- Shared result elements ---
  var resultsPanel = document.getElementById("results-panel");
  var categoryCard = document.getElementById("category-card");
  var categoryHeading = document.getElementById("category-heading");
  var categoryBadge = document.getElementById("category-badge");
  var ghsi10Card = document.getElementById("ghsi10-card");
  var ghsi10Heading = document.getElementById("ghsi10-heading");
  var ghsi10Value = document.getElementById("ghsi10-value");
  var ghsi10Detail = document.getElementById("ghsi10-detail");
  var icecapValue = document.getElementById("icecap-value");
  var icecapDisutility = document.getElementById("icecap-disutility");
  var sf6dValue = document.getElementById("sf6d-value");
  var sf6dDisutility = document.getElementById("sf6d-disutility");

  // --- Tab switching ---
  function switchTab(activeIndex) {
    for (var i = 0; i < tabs.length; i++) {
      if (i === activeIndex) {
        tabs[i].tab.classList.add("active");
        tabs[i].panel.classList.add("active");
      } else {
        tabs[i].tab.classList.remove("active");
        tabs[i].panel.classList.remove("active");
      }
    }
    resultsPanel.classList.remove("visible");
  }

  tabs[0].tab.addEventListener("click", function() { switchTab(0); });
  tabs[1].tab.addEventListener("click", function() { switchTab(1); });
  tabs[2].tab.addEventListener("click", function() { switchTab(2); });

  // --- GHSI version form logic ---
  function getSelectedVersion() {
    for (var i = 0; i < versionRadios.length; i++) {
      if (versionRadios[i].checked) return versionRadios[i].value;
    }
    return "ghsi7";
  }

  function updateFormForVersion() {
    var version = getSelectedVersion();
    if (version === "ghsi3") {
      scoreLabel.textContent = "Enter your GHSI-3 score";
      scoreInput.max = 9;
      rangeHint.textContent = "Valid range: 0 \\u2013 9";
    } else if (version === "ghsi7") {
      scoreLabel.textContent = "Enter your GHSI-7 score";
      scoreInput.max = 21;
      rangeHint.textContent = "Valid range: 0 \\u2013 21";
    } else {
      scoreLabel.textContent = "Enter your GHSI-10 score";
      scoreInput.max = 30;
      rangeHint.textContent = "Valid range: 0 \\u2013 30";
    }
    scoreInput.value = "";
    resultsPanel.classList.remove("visible");
    errorMsg.classList.remove("visible");
  }

  for (var i = 0; i < versionRadios.length; i++) {
    versionRadios[i].addEventListener("change", updateFormForVersion);
  }

  // --- AO version form logic ---
  function getSelectedAoVersion() {
    for (var i = 0; i < aoVersionRadios.length; i++) {
      if (aoVersionRadios[i].checked) return aoVersionRadios[i].value;
    }
    return "ao7";
  }

  function updateAoFormForVersion() {
    var version = getSelectedAoVersion();
    if (version === "ao3") {
      aoScoreLabel.textContent = "Enter your GHSI-AO-3 score";
      aoScoreInput.max = 9;
      aoRangeHint.textContent = "Valid range: 0 \\u2013 9";
    } else if (version === "ao7") {
      aoScoreLabel.textContent = "Enter your GHSI-AO-7 score";
      aoScoreInput.max = 21;
      aoRangeHint.textContent = "Valid range: 0 \\u2013 21";
    } else {
      aoScoreLabel.textContent = "Enter your GHSI-AO-10 score";
      aoScoreInput.max = 30;
      aoRangeHint.textContent = "Valid range: 0 \\u2013 30";
    }
    aoScoreInput.value = "";
    resultsPanel.classList.remove("visible");
    aoErrorMsg.classList.remove("visible");
  }

  for (var i = 0; i < aoVersionRadios.length; i++) {
    aoVersionRadios[i].addEventListener("change", updateAoFormForVersion);
  }

  // --- Shared helpers ---
  function getCategoryClass(category) {
    var map = {
      "No Harm": "no-harm",
      "Low Harm": "low-harm",
      "Moderate Harm": "moderate-harm",
      "High Harm": "high-harm",
      "Severe Harm": "severe-harm"
    };
    return map[category] || "";
  }

  function formatNum(n, dp) {
    if (typeof dp === "undefined") dp = 2;
    return Number(n).toFixed(dp);
  }

  function displayResults(cat, equivalentScore, precise, lower, upper, showConversion, row, labelPrefix) {
    var prefix = labelPrefix || "GHSI";
    categoryHeading.textContent = prefix + " Harm Category";
    ghsi10Heading.textContent = prefix + "-10 Equivalent Score";

    var catClass = getCategoryClass(cat);
    categoryBadge.textContent = cat;
    categoryBadge.className = "category-badge badge-" + catClass;
    categoryCard.className = "result-card category-card category-" + catClass;

    if (showConversion) {
      ghsi10Card.style.display = "block";
      ghsi10Value.textContent = equivalentScore;
      ghsi10Detail.textContent = "Precise estimate: " + formatNum(precise) +
        " (95% CI: " + formatNum(lower) + " \\u2013 " + formatNum(upper) + ")";
    } else {
      ghsi10Card.style.display = "none";
    }

    icecapValue.textContent = formatNum(row.icecap);
    icecapDisutility.textContent = formatNum(row.icecap_dis);
    sf6dValue.textContent = formatNum(row.sf6d);
    sf6dDisutility.textContent = formatNum(row.sf6d_dis);

    resultsPanel.classList.add("visible");
    resultsPanel.scrollIntoView({ behavior: "smooth", block: "nearest" });
  }

  // --- GHSI convert ---
  function doConvert() {
    var version = getSelectedVersion();
    var rawVal = scoreInput.value.trim();

    if (rawVal === "") {
      showError(errorMsg, "Please enter a score.");
      return;
    }

    var score = parseInt(rawVal, 10);
    if (isNaN(score) || score !== parseFloat(rawVal)) {
      showError(errorMsg, "Please enter a whole number.");
      return;
    }

    var maxScore = (version === "ghsi3") ? 9 : (version === "ghsi7") ? 21 : 30;
    if (score < 0 || score > maxScore) {
      showError(errorMsg, "Score must be between 0 and " + maxScore + ".");
      return;
    }

    errorMsg.classList.remove("visible");

    var ghsi10Score;
    if (version === "ghsi3") {
      ghsi10Score = GHSI3_TO_GHSI10[score];
      if (ghsi10Score === undefined) {
        showError(errorMsg, "No GHSI-10 conversion available for this GHSI-3 score.");
        return;
      }
    } else if (version === "ghsi7") {
      ghsi10Score = GHSI7_TO_GHSI10[score];
    } else {
      ghsi10Score = score;
    }

    var row = LOOKUP[ghsi10Score];

    if (version === "ghsi3") {
      displayResults(row.category, ghsi10Score, row.ghsi3_10_precise, row.ghsi3_10_lower, row.ghsi3_10_upper, true, row, "GHSI");
    } else if (version === "ghsi7") {
      displayResults(row.category, ghsi10Score, row.ghsi7_10_precise, row.ghsi7_10_lower, row.ghsi7_10_upper, true, row, "GHSI");
    } else {
      displayResults(row.category, ghsi10Score, null, null, null, false, row, "GHSI");
    }
  }

  // --- AO convert ---
  function doAoConvert() {
    var version = getSelectedAoVersion();
    var rawVal = aoScoreInput.value.trim();

    if (rawVal === "") {
      showError(aoErrorMsg, "Please enter a score.");
      return;
    }

    var score = parseInt(rawVal, 10);
    if (isNaN(score) || score !== parseFloat(rawVal)) {
      showError(aoErrorMsg, "Please enter a whole number.");
      return;
    }

    var maxScore = (version === "ao3") ? 9 : (version === "ao7") ? 21 : 30;
    if (score < 0 || score > maxScore) {
      showError(aoErrorMsg, "Score must be between 0 and " + maxScore + ".");
      return;
    }

    aoErrorMsg.classList.remove("visible");

    var ao10Score;
    if (version === "ao3") {
      ao10Score = AO3_TO_AO10[score];
      if (ao10Score === undefined) {
        showError(aoErrorMsg, "No GHSI-AO-10 conversion available for this GHSI-AO-3 score.");
        return;
      }
    } else if (version === "ao7") {
      ao10Score = AO7_TO_AO10[score];
    } else {
      ao10Score = score;
    }

    var row = AO_LOOKUP[ao10Score];

    if (version === "ao3") {
      displayResults(row.category, ao10Score, row.ao3_10_precise, row.ao3_10_lower, row.ao3_10_upper, true, row, "GHSI-AO");
    } else if (version === "ao7") {
      displayResults(row.category, ao10Score, row.ao7_10_precise, row.ao7_10_lower, row.ao7_10_upper, true, row, "GHSI-AO");
    } else {
      displayResults(row.category, ao10Score, null, null, null, false, row, "GHSI-AO");
    }
  }

  // --- PGSI convert ---
  function doPgsiConvert() {
    var rawVal = pgsiScoreInput.value.trim();

    if (rawVal === "") {
      showError(pgsiErrorMsg, "Please enter a score.");
      return;
    }

    var score = parseInt(rawVal, 10);
    if (isNaN(score) || score !== parseFloat(rawVal)) {
      showError(pgsiErrorMsg, "Please enter a whole number.");
      return;
    }

    if (score < 0 || score > 27) {
      showError(pgsiErrorMsg, "Score must be between 0 and 27.");
      return;
    }

    pgsiErrorMsg.classList.remove("visible");

    var row = PGSI_BY_SCORE[score];
    if (!row) {
      showError(pgsiErrorMsg, "No GHSI-10 conversion available for this PGSI score.");
      return;
    }

    displayResults(row.category, row.ghsi10, row.pgsi_10_precise, row.pgsi_10_lower, row.pgsi_10_upper, true, row, "GHSI");
  }

  function showError(el, msg) {
    el.textContent = msg;
    el.classList.add("visible");
    resultsPanel.classList.remove("visible");
  }

  convertBtn.addEventListener("click", doConvert);
  aoConvertBtn.addEventListener("click", doAoConvert);
  pgsiConvertBtn.addEventListener("click", doPgsiConvert);

  scoreInput.addEventListener("keydown", function(e) {
    if (e.key === "Enter") {
      e.preventDefault();
      doConvert();
    }
  });

  aoScoreInput.addEventListener("keydown", function(e) {
    if (e.key === "Enter") {
      e.preventDefault();
      doAoConvert();
    }
  });

  pgsiScoreInput.addEventListener("keydown", function(e) {
    if (e.key === "Enter") {
      e.preventDefault();
      doPgsiConvert();
    }
  });

})();
</script>
'))
```
