---
title: "GHSI Score Calculator"
description: |
  Calculate your transformed GHSI-SF score
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(htmlwidgets)
```

# Gambling Harms Severity Index Calculator

Enter your raw GHSI score to see your transformed score and interpretation.

``` {r}
# Create a simpler HTML structure with inline JavaScript
htmltools::HTML('
<div class="calculator-container" style="max-width: 600px; margin: 20px auto; padding: 20px; border: 1px solid #ccc; border-radius: 5px;">
  <h3 style="margin-top: 0;">Score Calculator</h3>
  <div class="form-group">
    <label for="rawScore">Enter your raw score (0-30):</label>
    <input type="number" id="rawScore" min="0" max="30" value="0" style="width: 100%; padding: 8px; margin: 10px 0; box-sizing: border-box;">
  </div>
  <button id="calculateBtn" style="background-color: #698F3F; color: white; border: none; padding: 10px 15px; cursor: pointer; border-radius: 4px;">Calculate</button>
  <div id="results" style="margin-top: 20px; padding: 15px; background-color: #f8f8f8; border-radius: 4px; display: none;">
    <h4 style="margin-top: 0;">Results:</h4>
    <p>Transformed Score: <span id="transformedScore" style="font-weight: bold;"></span></p>
    <p>Severity Level: <span id="severityLevel" style="font-weight: bold;"></span></p>
    <div id="interpretationText" style="margin-top: 10px; font-style: italic;"></div>
  </div>
</div>

<script>
document.addEventListener("DOMContentLoaded", function() {
  var rawScoreInput = document.getElementById("rawScore");
  var calculateBtn = document.getElementById("calculateBtn");
  var results = document.getElementById("results");
  var transformedScoreEl = document.getElementById("transformedScore");
  var severityLevelEl = document.getElementById("severityLevel");
  var interpretationTextEl = document.getElementById("interpretationText");
  
  calculateBtn.addEventListener("click", function() {
    var rawScore = parseFloat(rawScoreInput.value);
    
    // Validate input
    if (isNaN(rawScore) || rawScore < 0 || rawScore > 30) {
      alert("Please enter a valid score between 0 and 30");
      return;
    }
    
    // Calculate transformed score using your formula
    // Replace this with your actual transformation formula
    var transformedScore = (rawScore * 0.8).toFixed(1);
    
    // Determine severity level
    var severityLevel = "";
    var interpretationText = "";
    
    if (rawScore <= 5) {
      severityLevel = "Minimal";
      interpretationText = "This score suggests minimal gambling-related harms.";
    } else if (rawScore <= 10) {
      severityLevel = "Low";
      interpretationText = "This score suggests low levels of gambling-related harms.";
    } else if (rawScore <= 15) {
      severityLevel = "Moderate";
      interpretationText = "This score suggests moderate levels of gambling-related harms.";
    } else if (rawScore <= 20) {
      severityLevel = "Moderately Severe";
      interpretationText = "This score suggests moderately severe gambling-related harms.";
    } else {
      severityLevel = "Severe";
      interpretationText = "This score suggests severe gambling-related harms.";
    }
    
    // Update results
    transformedScoreEl.textContent = transformedScore;
    severityLevelEl.textContent = severityLevel;
    interpretationTextEl.textContent = interpretationText;
    
    // Show results
    results.style.display = "block";
  });
});
</script>
')
```

# About the GHSI Score

The Gambling Harms Severity Index (GHSI) measures gambling-related harm severity. The transformation from raw scores to the GHSI metric has been validated through Rasch analysis to create an interval-level measure.

## Key Interpretations:

- **Minimal (0-5)**: Few or no gambling-related harms
- **Low (6-10)**: Minor harms with limited impact on wellbeing
- **Moderate (11-15)**: Noticeable harms affecting multiple areas of life
- **Moderately Severe (16-20)**: Significant harms with substantial impact on wellbeing
- **Severe (21-30)**: Extensive harms with major consequences across multiple domains
