---
title: "Gambling Harms Severity Index Calculator"
description: |
  Calculate your transformed GHSI-SF score.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(htmlwidgets)
library(htmltools)
library(jsonlite)
library(tidyverse)
```

Enter your raw GHSI score to see your transformed score and interpretation.

```{r widget}
# Create your Rasch conversion table
rasch_table <- read.csv("data/all_pgsi_1+_SCFILE_2025-02-04.csv") %>% 
  rename(
    raw_score = SCORE,
    measure = MEASURE,
    standard_error = `S.E.`) %>% 
  dplyr::select(raw_score, measure, standard_error)

# Convert to JSON and create the complete HTML with the JSON data embedded directly
rasch_json <- jsonlite::toJSON(rasch_table)

# Create the HTML widget using htmltools::HTML for direct insertion
htmltools::HTML(paste0('
<div class="calculator-container" style="max-width: 600px; margin: 20px auto; padding: 20px; border: 1px solid #ccc; border-radius: 5px;">
  <h3 style="margin-top: 0;">Rasch Measure Calculator</h3>
  <div class="form-group">
    <label for="rawScore">Enter your raw score (0-27):</label>
    <input type="number" id="rawScore" min="0" max="27" value="0" style="width: 100%; padding: 8px; margin: 10px 0; box-sizing: border-box;">
  </div>
  <button id="calculateBtn" style="background-color: #698F3F; color: white; border: none; padding: 10px 15px; cursor: pointer; border-radius: 4px;">Calculate</button>
  <div id="results" style="margin-top: 20px; padding: 15px; background-color: #f8f8f8; border-radius: 4px; display: none;">
    <h4 style="margin-top: 0;">Results:</h4>
    <p>Raw Score: <span id="rawScoreDisplay" style="font-weight: bold;"></span></p>
    <p>Measure (logits): <span id="measureScore" style="font-weight: bold;"></span></p>
    
    <!-- Data Points Visualization using HTML -->
    <div style="margin: 30px 0;">
      <h5>Raw Score to Measure Relationship</h5>
      <div style="padding: 0 45px 45px 45px;">
        <div id="curveContainer" style="position: relative; width: 100%; height: 200px; border-left: 1px solid #999; border-bottom: 1px solid #999; margin: 10px 0 0 0; background-color: #f9f9f9;">
          <!-- Points will be added dynamically by JavaScript -->
          
          <!-- User position marker -->
          <div id="positionDot" style="position: absolute; width: 8px; height: 8px; background-color: #e74c3c; border-radius: 50%; display: none; transform: translate(-50%, -50%); z-index: 10;"></div>
          
          <!-- Guide lines -->
          <div id="horizontalGuideLine" style="position: absolute; height: 1px; background-color: transparent; border-top: 1px dashed #999; display: none; z-index: 5;"></div>
          <div id="verticalGuideLine" style="position: absolute; width: 1px; background-color: transparent; border-left: 1px dashed #999; display: none; z-index: 5;"></div>
          
          <!-- Axis labels -->
          <div style="position: absolute; top: 90px; left: -40px; transform: rotate(-90deg); transform-origin: left center; font-size: 12px; white-space: nowrap;">Raw Score</div>
          <div style="position: absolute; bottom: -30px; right: 0; left: 0; text-align: center; font-size: 12px;">Rasch Measure (logits)</div>
          
          <!-- Y axis ticks -->
          <div style="position: absolute; top: 0%; left: -25px; font-size: 10px; transform: translateY(-50%);">27</div>
          <div style="position: absolute; top: 25%; left: -25px; font-size: 10px; transform: translateY(-50%);">20</div>
          <div style="position: absolute; top: 50%; left: -25px; font-size: 10px; transform: translateY(-50%);">13</div>
          <div style="position: absolute; top: 75%; left: -25px; font-size: 10px; transform: translateY(-50%);">7</div>
          <div style="position: absolute; top: 100%; left: -25px; font-size: 10px; transform: translateY(-50%);">0</div>
          
          <!-- X axis ticks -->
          <div style="position: absolute; bottom: -20px; left: 0%; font-size: 10px; transform: translateX(-50%);">-5</div>
          <div style="position: absolute; bottom: -20px; left: 20%; font-size: 10px; transform: translateX(-50%);">-3</div>
          <div style="position: absolute; bottom: -20px; left: 40%; font-size: 10px; transform: translateX(-50%);">-1</div>
          <div style="position: absolute; bottom: -20px; left: 60%; font-size: 10px; transform: translateX(-50%);">1</div>
          <div style="position: absolute; bottom: -20px; left: 80%; font-size: 10px; transform: translateX(-50%);">3</div>
        </div>
      </div>
      
      <p style="margin-top: 20px;">Severity Level: <span id="severityLevel" style="font-weight: bold;"></span></p>
      <div id="interpretationText" style="margin-top: 10px; font-style: italic;"></div>
    </div>
    
    <!-- Wellbeing Decrement Visualization -->
    <div style="margin: 30px 0;">
      <h5>Wellbeing Decrement</h5>
      <div style="position: relative; width: 100%; height: 40px; margin: 20px 0 40px 0;">
        <!-- Bar background -->
        <div style="position: absolute; top: 0; left: 0; width: 100%; height: 20px; background: linear-gradient(to right, #e5f7e5, #ffcdd2); border-radius: 10px;"></div>
        
        <!-- Decrement indicator bar -->
        <div id="wellbeingBar" style="position: absolute; top: 0; left: 0; height: 20px; background-color: rgba(231, 76, 60, 0.7); border-radius: 10px 0 0 10px; width: 0;"></div>
        
        <!-- Scale labels -->
        <div style="position: absolute; bottom: -25px; left: 0; width: 100%; display: flex; justify-content: space-between; font-size: 12px;">
          <div>0</div>
          <div>-1</div>
          <div>-2</div>
          <div>-3</div>
          <div>-4</div>
          <div>-5</div>
        </div>
        
        <!-- Marker arrow -->
        <div id="wellbeingMarker" style="position: absolute; top: -15px; left: 0; width: 0; height: 0; border-left: 8px solid transparent; border-right: 8px solid transparent; border-top: 12px solid #333; transform: translateX(-50%); display: none;"></div>
      </div>
      
      <p>Wellbeing Decrement: <span id="wellbeing" style="font-weight: bold;"></span></p>
      <div id="wellbeingText" style="margin-top: 10px; font-style: italic;"></div>
    </div>
  </div>
</div>

<script>
// Immediately execute this function to avoid global scope issues
(function() {
  // Add an event listener for when the DOM is fully loaded
  document.addEventListener("DOMContentLoaded", function() {
    var rawScoreInput = document.getElementById("rawScore");
    var calculateBtn = document.getElementById("calculateBtn");
    var results = document.getElementById("results");
    var rawScoreDisplay = document.getElementById("rawScoreDisplay");
    var measureScoreEl = document.getElementById("measureScore");
    var severityLevelEl = document.getElementById("severityLevel");
    var interpretationTextEl = document.getElementById("interpretationText");
    var wellbeingEl = document.getElementById("wellbeing");
    var wellbeingTextEl = document.getElementById("wellbeingText");
    var positionDot = document.getElementById("positionDot");
    var horizontalGuideLine = document.getElementById("horizontalGuideLine");
    var verticalGuideLine = document.getElementById("verticalGuideLine");
    var wellbeingBar = document.getElementById("wellbeingBar");
    var wellbeingMarker = document.getElementById("wellbeingMarker");
    var curveContainer = document.getElementById("curveContainer");
    
    // Embed the Rasch data directly in the JavaScript
    var raschData = ', rasch_json, ';
    
    // Constants for scale conversion
    var scaleMin = -5;
    var scaleMax = 4;
    var scaleRange = scaleMax - scaleMin;
    var maxRawScore = 27;
    
    // Sort data by raw score to ensure proper ordering
    raschData.sort(function(a, b) {
      return a.raw_score - b.raw_score;
    });
    
    // Create data points
    function createDataPoints() {
      // Clear any existing points
      var existingPoints = curveContainer.querySelectorAll(".data-point");
      existingPoints.forEach(function(point) {
        curveContainer.removeChild(point);
      });
      
      // Add data points
      for (var i = 0; i < raschData.length; i++) {
        var entry = raschData[i];
        
        // Calculate position percentages
        var xPercent = ((entry.measure - scaleMin) / scaleRange) * 100;
        var yPercent = 100 - ((entry.raw_score / maxRawScore) * 100);
        
        // Create point element
        var point = document.createElement("div");
        point.className = "data-point";
        point.style.position = "absolute";
        point.style.width = "6px";
        point.style.height = "6px";
        point.style.backgroundColor = "#698F3F";
        point.style.borderRadius = "50%";
        point.style.left = xPercent + "%";
        point.style.top = yPercent + "%";
        point.style.transform = "translate(-50%, -50%)";
        point.style.zIndex = "2";
        
        // Add to container
        curveContainer.appendChild(point);
      }
    }
    
    // Create the data points immediately
    createDataPoints();
    
    // Add click handler for the calculate button
    calculateBtn.addEventListener("click", function() {
      var rawScore = parseInt(rawScoreInput.value);
      
      // Validate input
      if (isNaN(rawScore) || rawScore < 0 || rawScore > 27) {
        alert("Please enter a valid score between 0 and 27");
        return;
      }
      
      // Find the matching entry in raschData
      var entry = null;
      for (var i = 0; i < raschData.length; i++) {
        if (raschData[i].raw_score === rawScore) {
          entry = raschData[i];
          break;
        }
      }
      
      if (!entry) {
        alert("Error: Score not found in conversion table");
        return;
      }
      
      var measure = entry.measure;
      
      // Determine severity level
      var severityLevel = "";
      var interpretationText = "";
      
      // Define severity levels based on the logit measure
      if (measure < -2.0) {
        severityLevel = "Minimal";
        interpretationText = "This level indicates minimal gambling-related harms. Few to no significant problems related to gambling are present.";
      } else if (measure < -1.0) {
        severityLevel = "Low";
        interpretationText = "This level indicates low gambling-related harms. Some minor problems may be present but they have limited impact on daily functioning.";
      } else if (measure < 0.5) {
        severityLevel = "Moderate";
        interpretationText = "This level indicates moderate gambling-related harms with noticeable impact on some areas of life.";
      } else if (measure < 2.0) {
        severityLevel = "Moderately Severe";
        interpretationText = "This level indicates significant gambling-related harms affecting multiple areas of life.";
      } else {
        severityLevel = "Severe";
        interpretationText = "This level indicates severe gambling-related harms with substantial negative impacts across most areas of life.";
      }
      
      // Determine wellbeing level
      var wellbeing = "";
      var wellbeingText = "";
      var wellbeingValue = 0;
      
      // Define wellbeing levels based on the raw score
      if (rawScore < 1) {
        wellbeing = "No Decrement";
        wellbeingText = "This level indicates no decrement to Mental Wellbeing on the WEMWBS inventory.";
        wellbeingValue = 0;
      } else if (rawScore < 3) {
        wellbeing = "-2.14";
        wellbeingText = "This level indicates a reduction in Mental Wellbeing on the WEMWBS that could be translated to a depression indicator of Possible or Mild Depression.";
        wellbeingValue = 2.14;
      } else if (rawScore < 8) {
        wellbeing = "-4.38";
        wellbeingText = "This level indicates a reduction in Mental Wellbeing on the WEMWBS that could be translated to a depression indicator of Possible or Mild Depression.";
        wellbeingValue = 4.38;
      } else {
        wellbeing = "-4.01";
        wellbeingText = "This level indicates a reduction in Mental Wellbeing on the WEMWBS that could be translated to a depression indicator of Possible or Mild Depression.";
        wellbeingValue = 4.01;
      }
      
      // Update results
      rawScoreDisplay.textContent = rawScore;
      measureScoreEl.textContent = measure.toFixed(2);
      severityLevelEl.textContent = severityLevel;
      interpretationTextEl.textContent = interpretationText;
      wellbeingEl.textContent = wellbeing;
      wellbeingTextEl.textContent = wellbeingText;
      
      // Calculate position for visualizations
      var xPercent = ((measure - scaleMin) / scaleRange) * 100;
      var yPercent = 100 - ((rawScore / maxRawScore) * 100);
      
      // Position the dot at the intersection
      positionDot.style.left = xPercent + "%";
      positionDot.style.top = yPercent + "%";
      positionDot.style.display = "block";
      
      // Position horizontal guide line (from y-axis to the dot)
      horizontalGuideLine.style.top = yPercent + "%";
      horizontalGuideLine.style.left = "0";
      horizontalGuideLine.style.width = xPercent + "%";
      horizontalGuideLine.style.display = "block";
      
      // Position vertical guide line (from dot to x-axis)
      verticalGuideLine.style.left = xPercent + "%";
      verticalGuideLine.style.top = yPercent + "%";
      verticalGuideLine.style.height = (100 - yPercent) + "%";
      verticalGuideLine.style.display = "block";
      
      // Update wellbeing visualization
      var wellbeingPercent = (wellbeingValue / 5) * 100;
      wellbeingBar.style.width = wellbeingPercent + "%";
      wellbeingMarker.style.left = wellbeingPercent + "%";
      wellbeingMarker.style.display = "block";
      
      // Show results
      results.style.display = "block";
    });
  });
})();
</script>
'))
```



# About the GHSI Score

The Gambling Harms Severity Index (GHSI) measures gambling-related harm severity. The transformation from raw scores to the GHSI metric has been validated through Rasch analysis to create an interval-level measure.

## Key Interpretations:

- **Minimal (0-5)**: Few or no gambling-related harms
- **Low (6-10)**: Minor harms with limited impact on wellbeing
- **Moderate (11-15)**: Noticeable harms affecting multiple areas of life
- **Moderately Severe (16-20)**: Significant harms with substantial impact on wellbeing
- **Severe (21-30)**: Extensive harms with major consequences across multiple domains
