---
title: "Gambling Questionnaires Database"
description: |
  An overview of Gambling Harms Measures searchable database of gambling measurement tools
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DT)
library(dplyr)

# Read the full dataset
items <- read.csv("data/Gambling_Harms_Measure_Item_Bank_2024-12-11.csv", 
                  stringsAsFactors = FALSE,
                  check.names = F)


# Create a summary dataframe with one row per measure
measures_summary <- items %>%
  group_by(`Scale Name`) %>%
  summarize(
    Abbreviation = first(`Scale Abreviation`),
    `Number of Items` = n(),
    Authors = first(Authors),
    `Main Components` = paste(unique(`Harm Component`), collapse = ", ")
  ) %>%
  arrange(desc(`Abbreviation`))
```

# Gambling Measurement Tools Database

This database contains **`r nrow(measures_summary)` different gambling assessment measures** with a total of **`r nrow(items)` individual items**. You can explore this database in two different ways:

## Gambling Harms Measures Overview

```{r}
datatable(
  measures_summary,
  extensions = c('Buttons', 'Responsive'),
  options = list(
    dom = 'Bfrtip',
    buttons = list(list(
      extend = 'collection',
      buttons = c('csv', 'excel', 'pdf'),
      text = "Download")),
    pageLength = 12,
    autoWidth = TRUE,
    scrollX = TRUE
  ),
  rownames = FALSE,
  escape = FALSE,
)
```

```{r, echo=FALSE}
# If you want to add additional information or citations about these questionnaires
```


## Full Database
The complete database containing all **`r nrow(items)` individual items** items across all of the measures is available on our OSF repository. 

[View Full Item Database on OSF](https://osf.io)

The OSF repository includes:

- Complete item text for all measures
- Response options and scoring information
- Detailed harm component categorizations
- Full citations and measure information
- Downloadable CSV and Excel formats

## About This Database

This database was compiled as part of the Gambling Harms Severity Index project. If you would like to suggest additions or corrections to this database, please [contact us](mailto:ryan.statton@plymouth.ac.uk).

---

Last updated: `r format(Sys.Date(), "%B %d, %Y")`