---
title: "GHSI Score Converter"
description: "Convert GHSI-7 and GHSI-10 scores to harm categories, ICECAP-A and SF-6D
  tariffs.\n"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(jsonlite)
library(tidyverse)

# Read lookup table -- update this CSV to change the conversion data
lookup <- read_csv("data/GHSI_Rasch_Lookup_2026-02-06.csv", show_col_types = FALSE)

# Build JSON array for JavaScript, indexed by GHSI10_estimate (0-30)
js_rows <- lookup %>%
  arrange(GHSI10_estimate) %>%
  rowwise() %>%
  mutate(
    js = paste0(
      '{ ghsi7: ', ifelse(is.na(GHSI7_score), 'null', GHSI7_score),
      ', ghsi10_precise: ', ifelse(is.na(GHSI10_precise), 'null', sprintf("%.2f", GHSI10_precise)),
      ', ghsi10_lower: ', ifelse(is.na(GHSI10_lower), 'null', sprintf("%.2f", GHSI10_lower)),
      ', ghsi10_upper: ', ifelse(is.na(GHSI10_upper), 'null', sprintf("%.2f", GHSI10_upper)),
      ', category: "', GHSI_Category, '"',
      ', icecap: ', sprintf("%.2f", ICECAP),
      ', icecap_dis: ', sprintf("%.2f", ICECAP_disutility),
      ', sf6d: ', sprintf("%.2f", SF6D),
      ', sf6d_dis: ', sprintf("%.2f", SF6D_disutility),
      ' }'
    )
  ) %>%
  pull(js)

lookup_json <- paste0("[\n    ", paste(js_rows, collapse = ",\n    "), "\n  ]")
```

This tool converts scores from the **GHSI-7** (7-item) or **GHSI-10** (10-item) Gambling Harms Severity Index into a GHSI harm category and estimated health utility tariffs on the [ICECAP-A](https://www.bristol.ac.uk/population-health-sciences/projects/icecap/icecap-a/) and SF-6D scales. If you enter a GHSI-7 score, it will first be converted to a GHSI-10 equivalent.

<style type="text/css">
.converter-container {
  max-width: 680px;
  margin: 0 auto;
  padding: 0 1rem;
}
.converter-form {
  background: #fff9ef;
  border: 1px solid rgba(0, 0, 0, 0.1);
  border-radius: 8px;
  padding: 2rem;
  margin-bottom: 2rem;
}
.form-group {
  margin-bottom: 1.5rem;
}
.form-group label {
  display: block;
  font-family: "Hanken Grotesk", sans-serif;
  font-weight: 600;
  font-size: 0.95rem;
  margin-bottom: 0.5rem;
  color: #252323;
}
.radio-group {
  display: flex;
  gap: 1.5rem;
  margin-top: 0.25rem;
}
.radio-group label {
  display: flex;
  align-items: center;
  gap: 0.4rem;
  font-weight: 400;
  cursor: pointer;
  font-size: 1rem;
}
.radio-group input[type="radio"] {
  accent-color: #EB6534;
  width: 16px;
  height: 16px;
  cursor: pointer;
}
.score-input-row {
  display: flex;
  align-items: center;
  gap: 1rem;
}
.score-input-row input[type="number"] {
  width: 100px;
  padding: 0.6rem 0.8rem;
  font-family: "Bitter", serif;
  font-size: 1.1rem;
  border: 2px solid rgba(0, 0, 0, 0.15);
  border-radius: 6px;
  background: white;
  color: #252323;
  transition: border-color 0.2s;
}
.score-input-row input[type="number"]:focus {
  outline: none;
  border-color: #EB6534;
}
.score-range-hint {
  font-size: 0.85rem;
  color: rgba(37, 35, 35, 0.6);
}
.convert-btn {
  font-family: "Hanken Grotesk", sans-serif;
  padding: 0.75rem 2rem;
  background-color: #698F3F;
  color: #E6EFE9;
  border: none;
  border-radius: 6px;
  font-size: 1rem;
  font-weight: 600;
  cursor: pointer;
  transition: all 0.2s ease;
  display: block;
  width: 100%;
}
.convert-btn:hover {
  background-color: #5a7835;
  transform: translateY(-1px);
  box-shadow: 0 4px 8px rgba(105, 143, 63, 0.3);
}
.convert-btn:active {
  transform: translateY(0);
}
.results-panel {
  display: none;
  margin-top: 2rem;
}
.results-panel.visible {
  display: block;
}
.result-card {
  background: white;
  border: 1px solid rgba(0, 0, 0, 0.1);
  border-radius: 8px;
  padding: 1.5rem 2rem;
  margin-bottom: 1rem;
  border-left: 4px solid #698F3F;
}
.result-card h3 {
  font-family: "Hanken Grotesk", sans-serif;
  font-size: 0.85rem;
  text-transform: uppercase;
  letter-spacing: 0.05em;
  color: rgba(37, 35, 35, 0.5);
  margin: 0 0 0.25rem 0;
  font-weight: 600;
}
.result-card .result-value {
  font-family: "Bitter", serif;
  font-size: 1.4rem;
  font-weight: 600;
  color: #252323;
  margin: 0;
}
.result-card .result-detail {
  font-size: 0.9rem;
  color: rgba(37, 35, 35, 0.65);
  margin: 0.25rem 0 0 0;
}
.result-card.category-card {
  border-left-color: #EB6534;
}
.category-no-harm { border-left-color: #698F3F; }
.category-low-harm { border-left-color: #E8B931; }
.category-moderate-harm { border-left-color: #EB6534; }
.category-high-harm { border-left-color: #C1292E; }
.category-severe-harm { border-left-color: #6B1D24; }
.category-badge {
  display: inline-block;
  padding: 0.25rem 0.75rem;
  border-radius: 4px;
  font-family: "Hanken Grotesk", sans-serif;
  font-weight: 600;
  font-size: 1rem;
  color: white;
}
.badge-no-harm { background-color: #698F3F; }
.badge-low-harm { background-color: #E8B931; color: #252323; }
.badge-moderate-harm { background-color: #EB6534; }
.badge-high-harm { background-color: #C1292E; }
.badge-severe-harm { background-color: #6B1D24; }
.results-grid {
  display: grid;
  grid-template-columns: 1fr 1fr;
  gap: 1rem;
}
@media (max-width: 600px) {
  .results-grid {
    grid-template-columns: 1fr;
  }
  .score-input-row {
    flex-direction: column;
    align-items: flex-start;
  }
}
.ghsi10-conversion-note {
  font-size: 0.9rem;
  color: rgba(37, 35, 35, 0.65);
  margin-top: 0.15rem;
}
.error-message {
  color: #C1292E;
  font-size: 0.9rem;
  margin-top: 0.5rem;
  display: none;
}
.error-message.visible {
  display: block;
}
d-article .converter-container a,
d-article .converter-form a {
  border-bottom: none;
}
d-article .converter-container input,
d-article .converter-container button,
d-article .converter-container label {
  border-bottom: none;
}
</style>

<div class="converter-container">
<div class="converter-form">
<div class="form-group">
<label>Which GHSI version are you converting from?</label>
<div class="radio-group">
<label><input type="radio" name="ghsi-version" value="ghsi7" checked /> GHSI-7</label>
<label><input type="radio" name="ghsi-version" value="ghsi10" /> GHSI-10</label>
</div>
</div>
<div class="form-group">
<label for="score-input" id="score-label">Enter your GHSI-7 score</label>
<div class="score-input-row">
<input type="number" id="score-input" min="0" max="21" step="1" placeholder="0" />
<span class="score-range-hint" id="range-hint">Valid range: 0 &ndash; 21</span>
</div>
<p class="error-message" id="error-msg"></p>
</div>
<button class="convert-btn" id="convert-btn" type="button">Convert Score</button>
</div>
<div class="results-panel" id="results-panel">
<div class="result-card category-card" id="category-card">
<h3>GHSI Harm Category</h3>
<p class="result-value"><span class="category-badge" id="category-badge"></span></p>
</div>
<div class="result-card" id="ghsi10-card" style="display: none;">
<h3>GHSI-10 Equivalent Score</h3>
<p class="result-value" id="ghsi10-value"></p>
<p class="result-detail ghsi10-conversion-note" id="ghsi10-detail"></p>
</div>
<div class="results-grid">
<div class="result-card">
<h3>ICECAP-A Tariff</h3>
<p class="result-value" id="icecap-value"></p>
<p class="result-detail">Disutility: <span id="icecap-disutility"></span></p>
</div>
<div class="result-card">
<h3>SF-6D Tariff</h3>
<p class="result-value" id="sf6d-value"></p>
<p class="result-detail">Disutility: <span id="sf6d-disutility"></span></p>
</div>
</div>
</div>
</div>

## Understanding Health Utility and Disutility

Health utility is a way of measuring quality of life on a scale from 0 to 1. A score of 1 represents perfect health and wellbeing, while 0 represents a health state considered equivalent to death. These scores help us understand how much gambling harm affects someone's overall wellbeing in a standardised way that can be compared to other health conditions.

We use two different measures because gambling harm affects people in different ways. ICECAP-A captures your overall capability to live a fulfilling life, including things like relationships, stability, achievements, enjoyment, and independence. SF-6D focuses more specifically on health-related quality of life, covering physical functioning, pain, mental health, and energy levels. Healthy adults typically score around 0.86 on ICECAP-A and 0.90 on SF-6D ([see research publications](papers.html)).

Disutility simply means how much wellbeing someone has lost compared to a healthy person. Research shows that gambling harm affects capability wellbeing more than health-related quality of life alone, which is why ICECAP-A scores tend to be lower --- gambling disrupts many aspects of life beyond just physical and mental health symptoms ([see research publications](papers.html)).

```{r converter-js, results='asis'}
cat(paste0('
<script type="application/javascript">
(function() {

  var LOOKUP = ', lookup_json, ';

  var GHSI7_TO_GHSI10 = {};
  for (var i = 0; i < LOOKUP.length; i++) {
    if (LOOKUP[i].ghsi7 !== null) {
      GHSI7_TO_GHSI10[LOOKUP[i].ghsi7] = i;
    }
  }

  var versionRadios = document.querySelectorAll(\'input[name="ghsi-version"]\');
  var scoreInput = document.getElementById("score-input");
  var scoreLabel = document.getElementById("score-label");
  var rangeHint = document.getElementById("range-hint");
  var convertBtn = document.getElementById("convert-btn");
  var resultsPanel = document.getElementById("results-panel");
  var errorMsg = document.getElementById("error-msg");

  var categoryCard = document.getElementById("category-card");
  var categoryBadge = document.getElementById("category-badge");
  var ghsi10Card = document.getElementById("ghsi10-card");
  var ghsi10Value = document.getElementById("ghsi10-value");
  var ghsi10Detail = document.getElementById("ghsi10-detail");
  var icecapValue = document.getElementById("icecap-value");
  var icecapDisutility = document.getElementById("icecap-disutility");
  var sf6dValue = document.getElementById("sf6d-value");
  var sf6dDisutility = document.getElementById("sf6d-disutility");

  function getSelectedVersion() {
    for (var i = 0; i < versionRadios.length; i++) {
      if (versionRadios[i].checked) return versionRadios[i].value;
    }
    return "ghsi7";
  }

  function updateFormForVersion() {
    var version = getSelectedVersion();
    if (version === "ghsi7") {
      scoreLabel.textContent = "Enter your GHSI-7 score";
      scoreInput.max = 21;
      rangeHint.textContent = "Valid range: 0 \\u2013 21";
    } else {
      scoreLabel.textContent = "Enter your GHSI-10 score";
      scoreInput.max = 30;
      rangeHint.textContent = "Valid range: 0 \\u2013 30";
    }
    scoreInput.value = "";
    resultsPanel.classList.remove("visible");
    errorMsg.classList.remove("visible");
  }

  for (var i = 0; i < versionRadios.length; i++) {
    versionRadios[i].addEventListener("change", updateFormForVersion);
  }

  function getCategoryClass(category) {
    var map = {
      "No Harm": "no-harm",
      "Low Harm": "low-harm",
      "Moderate Harm": "moderate-harm",
      "High Harm": "high-harm",
      "Severe Harm": "severe-harm"
    };
    return map[category] || "";
  }

  function formatNum(n, dp) {
    if (typeof dp === "undefined") dp = 2;
    return Number(n).toFixed(dp);
  }

  function doConvert() {
    var version = getSelectedVersion();
    var rawVal = scoreInput.value.trim();

    if (rawVal === "") {
      showError("Please enter a score.");
      return;
    }

    var score = parseInt(rawVal, 10);
    if (isNaN(score) || score !== parseFloat(rawVal)) {
      showError("Please enter a whole number.");
      return;
    }

    var maxScore = (version === "ghsi7") ? 21 : 30;
    if (score < 0 || score > maxScore) {
      showError("Score must be between 0 and " + maxScore + ".");
      return;
    }

    errorMsg.classList.remove("visible");

    var ghsi10Score;
    if (version === "ghsi7") {
      ghsi10Score = GHSI7_TO_GHSI10[score];
    } else {
      ghsi10Score = score;
    }

    var row = LOOKUP[ghsi10Score];

    if (version === "ghsi7") {
      ghsi10Card.style.display = "block";
      ghsi10Value.textContent = ghsi10Score;
      ghsi10Detail.textContent = "Precise estimate: " + formatNum(row.ghsi10_precise) +
        " (95% CI: " + formatNum(row.ghsi10_lower) + " \\u2013 " + formatNum(row.ghsi10_upper) + ")";
    } else {
      ghsi10Card.style.display = "none";
    }

    var cat = row.category;
    var catClass = getCategoryClass(cat);
    categoryBadge.textContent = cat;
    categoryBadge.className = "category-badge badge-" + catClass;
    categoryCard.className = "result-card category-card category-" + catClass;

    icecapValue.textContent = formatNum(row.icecap);
    icecapDisutility.textContent = formatNum(row.icecap_dis);

    sf6dValue.textContent = formatNum(row.sf6d);
    sf6dDisutility.textContent = formatNum(row.sf6d_dis);

    resultsPanel.classList.add("visible");
    resultsPanel.scrollIntoView({ behavior: "smooth", block: "nearest" });
  }

  function showError(msg) {
    errorMsg.textContent = msg;
    errorMsg.classList.add("visible");
    resultsPanel.classList.remove("visible");
  }

  convertBtn.addEventListener("click", doConvert);

  scoreInput.addEventListener("keydown", function(e) {
    if (e.key === "Enter") {
      e.preventDefault();
      doConvert();
    }
  });

})();
</script>
'))
```
